The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-09 paper/sections/methods.tex
beam stuff updated
fix typo
typo

Quadrature points are selected so that $\samp{\Jnurbs}$ is of sufficient rank required to represent all control points. We achieve this by sampling over each knot span defined by the  B-splines, and find it effective to use the order of the NURBS as the number of quadrature points sampled in each knot span.
\ty{the number of samples may be different if order in the u direction and v differ, but I figured it was best to keep this simple.}

@@

\revise{Note that this approach yields compactly supported weight functions due to the cut-off parameter~(Eq.~8). 
Depending on this value, we obtain a range of system matrix sparsity patterns -- from fully dense to block sparse~(Fig.~9). 
Importantly, unlike other boundary-only approaches, our method is not guaranteed to produce dense system matrices.}

>>>>

Quadrature points are selected so that $\samp{\Jnurbs}$ is of sufficient rank required to represent all control points. We achieve this by sampling over each knot span defined by the  B-splines, and find it effective to use the order of the NURBS as the number of quadrature points sampled in each knot span. \revise{Positions and weights of the quadrature points in each span are chosen using Gauss-Lobatto quadrature.}
\ty{the number of samples may be different if order in the u direction and v differ, but I figured it was best to keep this simple.}

@@

\revise{Note that this approach yields compactly supported weight functions due to the cut-off parameter~(Eq.~8). 
Depending on this value, we obtain a range of system matrix sparsity patterns -- from fully dense to block sparse~(\reffig{stiffness_sparsity}). 
Importantly, unlike other boundary-only approaches, our method is not guaranteed to produce dense system matrices.}
